Since the first direct detection of gravitational waves by the LIGO scientific collaboration \citep{Abbott+2016_first_detection}, the number of black hole (BH) binaries and neutron star (NS) binaries detected by ground-based detectors has rapidly grown \citep{Abbott+2019_GWTC1,Abbott+2020_GWTC2}. These detections offer exciting insights into the evolution and endpoints of massive stars. The investigation of double compact object (DCO) population statistics will be an essential tool for predicting distributions of parameters that are observable with gravitational waves as well as constraining uncertainties in binary evolution. 

The Laser Interferometer Space Antenna (LISA, \citealp{Amaro-Seoane+2017}) will provide observations in an entirely new regime of gravitational waves. LISA will observe binaries at lower orbital frequencies than ground-based detectors ($10^{-5} \lesssim f / \unit{Hz} \lesssim 10^{-1}$) and so will enable the study of the gravitational wave mergers of supermassive black holes that are undetectable with ground-based detectors. However, this frequency regime is also of great interest for the detection of local stellar mass binaries during their inspiral phase. This means that LISA will be able to detect, and possibly localise a binary on the sky, far in advance of the merger, which presents an opportunity for both multimessenger detections to search for electromagnetic counterparts and multiband detections that would better constrain binary characteristics \citep[e.g.][]{Sesana+2016, Gerosa+2019}. In addition, DCOs may still have significant eccentricity in the LISA band and measurements of eccentricity may yield further constraints on binary evolution \citep[e.g.][]{Nelemans+2001, Breivik+2016, Antonini+2017, Rodriguez+2018}, differentiate between formation channels and distinguish between DCO types. The maximum distance at which stellar mass sources in LISA are detectable is significantly lower than in ground-based detectors since the gravitational wave signal is weaker during the inspiral phase than at the merger. This means that LISA stellar mass sources can only be detected in local galaxies, with the majority residing in the Milky Way. Therefore, these sources could be used as a probe for our galaxy's history and evolution \citep[e.g.][]{Korol+2019}.

Traditionally, investigations into detecting stellar mass sources with LISA focus on double white dwarf (WDWD) binaries \citep{Nelemans+2001,Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}. More recently, interest has grown in the detection of NS and BH binaries. Although these sources are rare, they could be useful for learning more about the evolution and endpoints of massive stars and thus we focus our paper on these sources.

For the purposes of this investigation, we consider only the classical isolated binary evolution channel \citep[e.g.][]{Tutukov+1973,Tutukov+1993,Kalogera+2007,Belczynski+2016} in which compact objects are formed through through highly non-conservative mass transfer or common envelope ejection. There are however several alternative proposed formation channels including: dynamical formation in dense star clusters \citep[e.g.][]{Sigurdsson+1993,PortegiesZwart+2000,Miller+2009,Rodriguez+2015} and (active) galactic nuclei discs \citep[e.g.][]{Morris+1993, Antonini+2016, McKernan+2020}, isolated hierarchical triple evolution involving Kozai-Lidov oscillations \citep[e.g.][]{Stephan+2016, Silsbee+2017,Antonini+2017} and chemically homogenous evolution through efficient rotational mixing \citep[e.g.][]{deMink+2009, deMink+2016,Marchant+2016,duBuisson+2020}.

Galactic double neutron star (NSNS) binaries have been observed with electromagnetic signals for several decades \citep[e.g.][]{Hulse+1975} and more recently the mergers of NSNS binaries with ground-based gravitational wave detectors have been observed \citep[e.g.][]{Abbott+2017_NSNS}. The detection of a NSNS in LISA in which at least one NS is a pulsar could connect these two populations as the binary could be observed from inspiral to merger. NSNS binaries are useful sources for understanding the origin of r-process elements \citep[e.g.][]{Eichler+1989} as well as the electromagnetic counterparts to gravitational wave signal such as kilonovae \citep[e.g.][]{Metzger+2017}, short gamma-ray bursts \citep[e.g.][]{Gompertz+2020}, radio emission \citep[e.g.][]{Hotokezaka+2016} and neutrinos \citep[e.g.][]{Kyutoku+2018}.

Double black hole (BHBH) binaries in the Milky Way present a greater observational challenge. To date, no BH has been observed to be in a binary with another compact object in the Milky Way and so LISA could provide the first detection of a Galactic BHBH binary. Moreover, the mass distribution of stellar mass black holes is still uncertain. The only confirmed BHs in our galaxy have been discovered as components of X-ray binaries with companion stars \citep[e.g.][]{Bolton+1972,Webster+1972}. This sample of BHs has masses mainly constrained between $5$ and $10 \unit{M_\odot}$ \citep{Corral-Santana+2016}, a stark contrast to the more massive BHs observed with LIGO/Virgo that tend to have masses concentrated around $30 \unit{M_{\odot}}$ \citep{Abbott+2020_GWTC2}. These observations indicate the presence of a lower mass gap (from $2$-$5 \unit{M_{\odot}}$) in which no black holes or neutron stars are observed \citep{Ozel+2010,Farr+2011} but its existence remains an open question \citep[e.g.][]{Woosley+2020}. Recently there has also been increased discussion over the maximum BH mass in our galaxy, with the claims of a $70 \unit{M_{\odot}}$ BH \citep{Liu+2019,Abdul-Masih+2020} and revised measurements of the mass of Cygnus X-1 \citep{Miller-Jones+2021}. A sample of BHBHs detected with LISA could possibly help to constrain these uncertainties in the stellar mass BH mass distribution.

One particularly interesting and elusive gravitational wave source is a black hole neutron star binary (BHNS). Of all the events detected by ground-based detectors, none can be confidently attributed to the merger of a black hole and a neutron star, though several events such as GW190425 and GW190814 have not been ruled out as a BHNS merger \citep{Abbott+2020_GW190425,Abbott+2020_GW190814}. Predictions for the merger rate of BHNSs range across three orders of magnitude \citep[e.g.][]{Abadie+2010, Broekgaarden+2021} so the number of detections in LISA will be important in reducing this uncertainty, thereby refining our understanding of the remnants and evolution of massive stars. These binaries are expected to have electromagnetic counterparts that can studied in the same way as NSNSs. A distinctly exciting possibility is the detection of a pulsar--BH system or millisecond pulsar--BH system \citep{Narayan+1991}. These systems could be observed not only by gravitational wave detectors, but also radio telescopes such as MeerKAT and SKA, which will help to constrain uncertain binary evolution processes \citep[e.g.][]{Pfahl+2005,Chattopadhyay+2020}.

The detection of DCOs with LISA has been investigated in many previous studies through a combination of population synthesis and Milky Way modelling. Previous studies that investigate BHBH, BHNS and NSNS binaries, as opposed to the numerous WDWD population, are still uncommon. Earlier work has used a variety of population synthesis codes, Milky Way models and LISA specifications, resulting in a wide range of predictions \citep{Nelemans+2001,Liu+2009,Belczynski+2010,Liu+2014,Lamberts+2019,Lau+2020,Breivik+2020,Sesana+2020}.

We build upon previous efforts but with several important improvements. We explore the effect of varying binary physics assumptions by repeating our analysis for 15 different models and comparing the effect on the detection rate and distributions of source parameters. We use a model for the Milky Way that is dependent on the chemical enrichment history and calibrated on the latest GAIA and APOGEE surveys \citep{GaiaCollaboration+2016,Majewski+2017,Frankel+2018}. In contrast to many previous works, we provide a full treatment of the eccentricity of detectable sources both for the inspiral evolution as well as gravitational wave signal during the LISA mission. Moreover, our binary population synthesis simulation is the most extensive of its kind to date, with 750 million simulated binaries (one million binaries for each of 50 metallicity bins and 15 physics variations) evolved to produce the DCO populations used in this work \citep{Broekgaarden+2021}. In addition, we use the adaptive sampling algorithm STROOPWAFEL \citep{Broekgaarden+2019} to further reduce our sampling noise.

In this paper, we present the most extensive simulations to date for predictions of the detection rate and distribution of binary properties (masses, frequency, eccentricity, distance, merger time) of BHBH, BHNS and NSNS binaries formed through isolated binary evolution in the Milky Way. We explore 15 different models of physical assumptions in our population synthesis model and how the changes in these assumptions alter our results. We also discuss the effect of extending the LISA mission length and the possibility of distinguishing detections.

Our paper is structured as follows. In Section~\ref{sec:method}, we describe our methods for synthesising a population of binaries, the variations of physical assumptions that we consider, how we simulate the Milky Way distribution of DCOs and our methods for calculating a detection rate for LISA. We present our main results in Section~\ref{sec:results}, analysing our findings for each DCO type and variation of physical assumptions. In Section~\ref{sec:discussion} we discuss these results. In Section~\ref{sec:compare_studies}, we compare and contrast our methods and findings to previous work and finish with our conclusions in Section~\ref{sec:conclusion}.

All data produced in this study is publicly available on Zenodo \href{https://doi.org/10.5281/zenodo.4574727}{\faFileCode}\footnote{\dots} \todo{add link} as is the population used in our simulations \href{https://doi.org/10.5281/zenodo.4574727}{\faFileCode}\footnote{\url{https://doi.org/10.5281/zenodo.4574727}}. We make all code used to produce our results available in a Github repository \href{https://github.com/TomWagg/detecting-DCOs-in-LISA}{\faGithub}\footnote{\url{https://github.com/TomWagg/detecting-DCOs-in-LISA}}. In addition, the repository contains step-by-step Jupyter notebooks that explain how to reproduce and change each figure in the paper. In a companion paper we present \href{https://legwork.readthedocs.io}{\texttt{LEGWORK}}\footnote{\url{https://legwork.readthedocs.io}}, a python package designed for making predictions for the detection of sources with LISA, which we use in this work.